Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-09-15 4_methodology/methodology.tex
no message

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}
Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this study, clustering is used to gather organizations based on their performance indicator data. In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. Since the number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, SSE values are plotted and user is asked to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

@@

\subsection{Recommendation Generation}
\label{subsec:recommendation-generation}
Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized. In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes. These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values. In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.

>>>>

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}
Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this study, clustering is used to gather organizations based on their performance indicator data. In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. Since the number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, \textit{Sum of Squared Error (SSE)} values are plotted and user is asked to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

@@

\subsection{Genarating Suggestions/Recommendations for Performance Improvement}
\label{subsec:recommendation-generation}
Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized. In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes. These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values. In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.
